% ============================================================
% TÀI LIỆU THAM KHẢO
% ============================================================
\chapter*{TÀI LIỆU THAM KHẢO}
\addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}

\begin{enumerate}[label={[\arabic*]}]

    \item Lewis, P., Perez, E., Piktus, A., Petroni, F., Karpukhin, V., Goyal, N., Küttler, H., Lewis, M., Yih, W., Rocktäschel, T., Riedel, S., \& Kiela, D. (2020). \textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}. Advances in Neural Information Processing Systems, 33, 9459--9474.

    \item Chen, J., Xiao, S., Zhang, P., Luo, K., Lian, D., \& Liu, Z. (2024). \textit{BGE M3-Embedding: Multi-Lingual, Multi-Functionality, Multi-Granularity Text Embeddings Through Self-Knowledge Distillation}. arXiv preprint arXiv:2402.03216.

    \item LangChain Team. (2024). \textit{LangGraph: Build Stateful, Multi-Actor Applications with LLMs}. \url{https://github.com/langchain-ai/langgraph}

    \item Google AI. (2024). \textit{Gemini 2.0 Flash: Next Generation Model}. \url{https://ai.google.dev/gemini-api}

    \item Cohere. (2024). \textit{Rerank Multilingual v3.0 API Documentation}. \url{https://docs.cohere.com/docs/rerank-2}

    \item FastAPI. (2024). \textit{FastAPI Documentation}. \url{https://fastapi.tiangolo.com/}

    \item Next.js Team. (2025). \textit{Next.js 16 Documentation}. \url{https://nextjs.org/docs}

    \item PostgreSQL Global Development Group. (2024). \textit{PostgreSQL 16 Documentation}. \url{https://www.postgresql.org/docs/16/}

    \item pgvector. (2024). \textit{Open-source vector similarity search for Postgres}. \url{https://github.com/pgvector/pgvector}

    \item Redis Ltd. (2024). \textit{Redis 7 Documentation}. \url{https://redis.io/docs/latest/}

    \item Apache Airflow. (2024). \textit{Airflow Documentation}. \url{https://airflow.apache.org/docs/}

    \item Playwright. (2024). \textit{Playwright for Python Documentation}. \url{https://playwright.dev/python/}

    \item Batdongsan.com.vn. (2024). \textit{Cổng thông tin bất động sản Việt Nam}. \url{https://batdongsan.com.vn/}

    \item SQLAlchemy. (2024). \textit{SQLAlchemy 2.0 Documentation}. \url{https://docs.sqlalchemy.org/en/20/}

    \item Pydantic. (2024). \textit{Pydantic V2 Documentation}. \url{https://docs.pydantic.dev/latest/}

    \item Tailwind CSS. (2025). \textit{Tailwind CSS v4 Documentation}. \url{https://tailwindcss.com/docs}

    \item Recharts. (2024). \textit{Recharts: Composable Charting Library}. \url{https://recharts.org/}

    \item Docker. (2024). \textit{Docker Compose Documentation}. \url{https://docs.docker.com/compose/}

\end{enumerate}

\newpage
